---
title: "Thesis EDA"
author: "Harrison DiStefano"
output:
  pdf_document: default
  html_notebook: default
---

```{r setup}
#knitr::opts_chunk$set(warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/harrison/Dropbox/Schoolwork/Thesis/Project/")
```


```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
```



```{r load data}
housing <- read.csv('data/processed.csv')
head(housing)
```


```{r data cleaning}
housing$DATE <- as.Date(housing$DATE, format = "%Y-%m-%d")
head(housing)
```


```{r}
housing %>%
  pivot_longer(c(MSPUS, MSACSR, S.P.Comp., Dividend, Earnings, Consumer.Price.Index.CPI),
               names_to = "var", values_to = "value") %>%
  ggplot(aes(x = DATE, y = value, group = 1)) +
  geom_line() +
  facet_grid(vars(var), scales = "free_y") +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
